# Fitting Aborts with step drift change on LED onset with Post-LED censoring

## The plan
The vanilla single bound proactive process fits well the LED off trials in the data. But there is peak in probability of aborts after LED onset.
We assume the simplest model where the drift increases abruptly once LED turns on. But there is a gap of ~40 ms between LED onset and its effect(shown in red).
This gap is due to the motor delay - the delay between hitting the bound and recording reaction time due to motor delays.
But there is another delay - afferent delay, which is the time taken for proactive processs to start after fixation onset.


% insert figure of data wrt LED onset

Instead of dealing with likelihood of this new drift change model, we follow this method
1. Fit only Pre-LED drift, bound and delay with LED off trials and LED on trials before LED onset
2. The LED on trials after LED onset are censored at LED onset.
3. Since we don't have a model for peak before 0.3 s, we are truncating the trials before 0.3s.

** Note about motor delay and afferent delay:**
We are not fitting afferent delay and motor delay seperately because for LED off trials, both the delays
can be merged as one. But for LED on trials, the motor delay is needed seperately to explain the gap between
LED onset and effect of LED(the 40ms gap). 

## Results:
1. Fitting Pre-LED drift, bound and delay with LED off trials and LED on trials before LED onset. 
And censoring LED on trials after LED onset at LED onset with VBMC, we get the following parameters:
% Insert corner plot

2. We run simulations with drift change at LED onset with different values of drift with motor delay(40ms) 
and find the most suitable post-LED drift value.
% Insert drift increase



## Code:
Simulator to simulate drift change at LED onset and motor delay
```python
dt = 1e-3; dB = np.sqrt(dt)
def simulate_v_change_pro(sim_params):
    v = sim_params['v']; theta = sim_params['theta']; new_v = sim_params['new_v']; aff = sim_params['aff'] 
    t_led = sim_params['t_led'];
    
    dv = 0
    motor_delay = 0.04 
    t = aff - motor_delay      
    while True:
        if t > t_led:
            v = new_v
        dv += v*dt + np.random.normal(0, dB)
        t += dt

        if dv > theta:
            return t + motor_delay, sim_params
```

The notebook link - https://github.com/rakaar/ddm_data/blob/main/fitting_aborts/V_A_step_jump_fit_censor_post_LED_real_data.ipynb

